Interoception Scale (Study 2) - Data Cleaning

### 2025-12-29 paper/manuscript.qmd
Internal consistency for tas was added
@DominiqueMakowski tas items are now reversed

The Toronto Alexithymia Scale TAS [TAS-20, @leising2009toronto] measures 3 Alexithymia dimensions with 20 items 5-point Likert scale (1 = *Strongly Disagree*, 5 = *Strongly Agree*: Difficulty Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and Externally Oriented Thinking (EOR).

>>>>

The Toronto Alexithymia Scale TAS [TAS-20, @leising2009toronto] measures 3 Alexithymia dimensions with 20 items 5-point Likert scale (1 = *Strongly Disagree*, 5 = *Strongly Agree*: Difficulty Identifying Feelings (DIF), Difficulty Describing Feelings (DDF), and Externally Oriented Thinking (EOT). In this study, the  TAS subscales showed poor to acceptable internal consistency: ωDIF = 0.77, ωDDF = 0.53 and ωEOT = 0.69.

### 2025-12-29 study2/analysis/1_cleaning.qmd
Internal consistency for tas was added
@DominiqueMakowski tas items are now reversed

- MAIA [x]
- MINT []
- BPQ [x]
- IAS [x]
- TAS-20 []
- B-ERS []
- CERQ-Short []
- CEFSA-14 []
- PI-18 []
- SILS (only one item)
- PHQ-4 []

@@

```{r}
ias <- df[,grepl("^IAS_", names(df))]
ias <- ias[,(names(ias) != "IAS_AttentionCheck_1")]
psych::omega(ias, nfactors = 1)

@@

# TODO: check if any reversed items in the following questionnaires
df <- compute_and_remove(df, name="TAS_EOT", method="mean")
df <- compute_and_remove(df, name="TAS_DDF", method="mean")
df <- compute_and_remove(df, name="TAS_DIF", method="mean")

>>>>

- MAIA [x]
- MINT []
- BPQ [x]
- IAS [x]
- TAS-20 [x]
- B-ERS []
- CERQ-Short []
- CEFSA-14 []
- PI-18 []
- SILS (only one item)
- PHQ-4 []

@@

```{r}
ias <- df[,grepl("^IAS_", names(df))]
ias <- ias[,(names(ias) != "IAS_AttentionCheck_1")]
psych::omega(ias, nfactors = 1)
```

```{r}
tas <- df |>
  select(starts_with("TAS_"))|>
  mutate(TAS_DIF_9 = 6 - TAS_DIF_9,
         TAS_DIF_13 = 6- TAS_DIF_13 , 
         TAS_EOT_15 = 6- TAS_EOT_15,
         TAS_EOT_18 = 6- TAS_EOT_18,
         TAS_EOT_19 = 6- TAS_EOT_19)

tas_eot <- tas[, grepl("^TAS_EOT_", names(tas))]
tas_ddf <-  tas[, grepl("^TAS_DDF_", names(tas))]
tas_dif <-  tas[, grepl("^TAS_DIF_", names(tas))]

psych::omega(tas_eot, nfactors = 1)
psych::omega(tas_ddf, nfactors = 1)
psych::omega(tas_dif, nfactors = 1)
```

@@

# TODO: check if any reversed items in the following questionnaires
#There are 5 items that are negatively keyed (items 9, 13, 15, 18 and 19) in the TAS

df <- df |>
  mutate(TAS_DIF_9 = 6 - TAS_DIF_9,
         TAS_DIF_13 = 6- TAS_DIF_13 , 
         TAS_EOT_15 = 6- TAS_EOT_15,
         TAS_EOT_18 = 6- TAS_EOT_18,
         TAS_EOT_19 = 6- TAS_EOT_19)

df <- compute_and_remove(df, name="TAS_EOT", method="mean")
df <- compute_and_remove(df, name="TAS_DDF", method="mean")
df <- compute_and_remove(df, name="TAS_DIF", method="mean")
